OCMu64: a solver for One-sided Crossing Minimization

### 2024-06-24 tex/description.tex
abstract

  We prove a number of novel reductions, and apply these in our solver OCMu64
  that directly uses branch-and-bound on the ordering of the vertices of $B$ and
  does not depend on ILP or SAT solvers.
\end{abstract}

>>>>

  We introduce the novel \emph{strongly fixed}, \emph{practically fixed}, and
  \emph{practically glued} reductions that maximally generalize some existing
  reductions.
  We apply these in our exact solver OCMu64, that directly uses branch-and-bound
  on the ordering of the vertices of $B$ and does not depend on ILP or SAT
  solvers.
\end{abstract}
